---
title: "DataViz Makeover 01"
description: |
  Objective: To create an alternative visualisation to understand Singapore's labour force in 2019. The original visualisation can be found in chart 6 of the report "Labour Force in Singapore 2019". (https://stats.mom.gov.sg/Pages/Labour-Force-Tables2019.aspx) 
author:
  - name: Angeline Jiang
    url: www.linkedin.com/in/angeline-jiang
date: 01-25-2021
output:
  distill::distill_article:
    toc: true
    toc_depth: 3
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# 1.0 Critiques and Suggestions for Current Visualisation

```{r, echo=FALSE, message=FALSE, out.width="120%", out.height="120%"}
library(knitr)
library(png)
img1_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/1_current visualisation.png"
include_graphics(img1_path)

```

## 1.1 Clarity

```{r, echo=FALSE, message=FALSE}
library("readxl")
library(kableExtra)

clarity <- read_excel("D:\\awljiang\\blog\\_posts\\2021-01-25-dataviz-makeover-01\\data\\1.1_clarity.xlsx")  
clarity_2 <- data.frame(clarity)

kbl(clarity_2) %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, border_right = T, width = "30em") %>% 
  column_spec(3, border_right = T, width = "30em")

```

## 1.2 Aesthetics

```{r, echo=FALSE, message=FALSE}
library("readxl")
library(kableExtra)

aesthetics <- read_excel("D:\\awljiang\\blog\\_posts\\2021-01-25-dataviz-makeover-01\\data\\1.2_aesthetics.xlsx")  
aesthetics_2 <- data.frame(aesthetics)

kbl(aesthetics_2) %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, border_right = T, width = "30em") %>% 
  column_spec(3, border_right = T, width = "30em")

```

#  2.0 Proposed Design

```{r, echo=FALSE, message=FALSE, out.width="120%", out.height="150%"}
library(knitr)
library(png)
img2_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/2_proposed design.png"
include_graphics(img2_path)

```

```{r, echo=FALSE, message=FALSE}
library("readxl")
library(kableExtra)

advantages <- read_excel("D:\\awljiang\\blog\\_posts\\2021-01-25-dataviz-makeover-01\\data\\2_advantages.xlsx")  
advantages_2 <- data.frame(advantages)

kbl(advantages_2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, border_right = T, width = "50em") 

```

# 3.0 Data Visualisation Steps 

## 3.1	Data Preparation

### 3.1.1	Resident Labour Force dataset

Step 1: Download "Table (7) Resident Labour Force Aged Fifteen Years and Over by Age and Sex, 2009 – 2019 (June)" from https://stats.mom.gov.sg/Pages/Labour-Force-Tables2019.aspx.

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3111_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.1.1.png"
include_graphics(img3111_path)

```

Step 2: Format the excel.
Unmerge the cells and remove unnecessary rows/columns.
Unmerge row 5,  rename column D as “Age” and delete columns A-C, F, H, J, L, N, P, R, T, V, X and Z (i.e. empty columns).
Delete rows 1-4, 6 and 19.
Rename the columns to include “(old)” and save the excel file.

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3112_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.1.2.png"
include_graphics(img3112_path)

```

Step 3: Open Tableau and connect to the excel file saved out in Step 2.

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3113_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.1.3.png"
include_graphics(img3113_path)

```

A view of the table in Tableau

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3114_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.1.4.png"
include_graphics(img3114_path)

```

Step 4: Pivot the table and rename the columns to “Year” and “Counts”.

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="150%", out.height="180%"}
library(knitr)
library(png)
img3115_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.1.5.png"
include_graphics(img3115_path)

```

Step 5: Right click on the drop down list under "Age" column, click "Create Group" to create 3 groups "15 - 24", "25 - 54" and "55 & over" by highlighting the subgroups and clicking on the "Group" button. Rename the group and repeat for the other 2 groups.

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="150%", out.height="150%"}
library(knitr)
library(png)
img3116_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.1.6.png"
include_graphics(img3116_path)

```

Step 6: Open a new worksheet in Tableau and drag "Age (group)" to Columns, "Year" to Rows and "Counts" to "Text" in the marks card. To obtain the row total, click on "Analysis" and drag "Totals" to "Rows Grand Totals".

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="90%", out.height="90%"}
library(knitr)
library(png)
img3117_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.1.7.png"
include_graphics(img3117_path)

```

Step 7: To obtain the share (%), click on "Sum(Counts)" in the marks card, and click on "Quick Table Calculations" and select "Percent of Total"

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3118_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.1.8.png"
include_graphics(img3118_path)

```

Step 8: Save this table for using in the visualisation by clicking on "Analysis" at the ribbon bar, select "View Data", followed by "Export All" and save into a folder.

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="150%", out.height="150%"}
library(knitr)
library(png)
img3119_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.1.9.png"
include_graphics(img3119_path)

```


### 3.1.2	Resident Labour Force Participation Rate dataset

Step 1: Download Labour Force Participation rate dataset from Singstat Table Builder (https://www.tablebuilder.singstat.gov.sg/publicfacing/mainMenu.action) by following the illustration below

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3121_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.2.1.png"
include_graphics(img3121_path)

```

Step 2: Open the excel file and copy the “outside labour force” table to the top right as shown below.
Rename the years “In” and “Out” to reflect the counts for in and out of labour force.
Delete rows 1-5, 7, 19 onward and rename column A to “Age”. Save the Excel file.

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3122_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.2.2.png"
include_graphics(img3122_path)

```

A view of the final table in Excel

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3123_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.2.3.png"
include_graphics(img3123_path)

```

Step 3: Open Tableau window and import the Excel saved in Step 2.

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3124_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.2.4.png"
include_graphics(img3124_path)

```

Step 4: Right click on the drop down list under "Age" column, click "Create Group" to create 3 groups "15 - 24", "25 - 54" and "55 & over" by highlighting the subgroups and clicking on the "Group" button. Rename the group and repeat for the other 2 groups.

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="90%", out.height="90%"}
library(knitr)
library(png)
img3125_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.2.5.png"
include_graphics(img3125_path)

```

Step 5: To obtain the labour force participation counts by the newly created age bands, click to open a new Tableau workbook. Drag "Measure Names" to "Columns", "Age (group)" to "Rows", and "Measure Values" to the Text marks card as shown below.

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3126_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.2.6.png"
include_graphics(img3126_path)

```

Step 6: Save this table by clicking on "Analysis" at the ribbon bar, select "View Data", followed by "Export All" and save into a folder.

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3127_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.2.7.png"
include_graphics(img3127_path)

```

Step 7: Drag the csv file saved in Step 6 into the polaris, right click the drop down list for the column "Year_In/Out" and click on Split. Rename the new columns "Year" and "In/Out".

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3128_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.2.8.png"
include_graphics(img3128_path)

```

Step 8: Open a new Tableau workbook, drag "In/Out" into "Columns", "Age (group)" and "Year" into "Rows" and "Counts" into the Text marks card. Click on "Analysis" and drag "Total" into "Row Grand Totals".

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="100%", out.height="100%"}
library(knitr)
library(png)
img3129_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.2.9.png"
include_graphics(img3129_path)

```

Step 9: To compute participation rate (%), click on the "Analysis" ribbon and select "Percentage of" and click "Row in Pane".

```{r, echo=FALSE, message=FALSE, out.width="50%", out.height="50%"}
library(knitr)
library(png)
img31210_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.2.10.png"
include_graphics(img31210_path)

```

Step 10: Save this table by clicking on "Analysis" at the ribbon bar, select "View Data", followed by "Export All" and save into a folder.

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img31211_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.2.11.png"
include_graphics(img31211_path)

```

Step 11: Open the csv file saved in step 10. To get the labour force participation rate, filter the column "In/Out" and delete rows that are "Out" ("In" refers to individuals in the labour force while "Out" refers to individuals not in the labour force). Save the file.

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img31212_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.2.12.png"
include_graphics(img31212_path)

```


### 3.1.3	Median Age of Labour Force

Step 1: Download "Table (2) Key Characteristics of Resident Labour Force, 2009 – 2019 (June)" from https://stats.mom.gov.sg/Pages/Labour-Force-Tables2019.aspx.

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3131_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.3.1.png"
include_graphics(img3131_path)

```

Step 2: Keep only columns B and G, delete rows 1-6 and 18 onward. Insert one row in row 1 and label “Year” and “Median Age”, to obtain the table below. Save the excel.

```{r, echo=FALSE, message=FALSE, out.width="25%", out.height="25%"}
library(knitr)
library(png)
img3132_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.1.3.2.png"
include_graphics(img3132_path)

```


## 3.2	Tableau Works

### 3.2.1	Importing and transforming data for creation of visualisation

Step 1: Import csv file for shares of resident labour force saved in 3.1.1 (step 8).

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3211_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.2.1.1.png"
include_graphics(img3211_path)

```

Step 2: Remove the old dataset and drag in the share file. Delete the first two columns, and rename last column to “Share”.

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3212_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.2.1.2.png"
include_graphics(img3212_path)

```

Step 3: To obtain shares in %, click on the drop down under "Share" column and select "Create Calculated Field". Type the formula shown below and click "OK". Rename the new column as "Shares (%)".

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3213_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.2.1.3.png"
include_graphics(img3213_path)

```

Step 4: Import participation rate csv file saved in 3.1.2 (step 11) by adding a connection.

```{r, echo=FALSE, message=FALSE, out.width="100%", out.height="100%"}
library(knitr)
library(png)
img3214_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.2.1.4.png"
include_graphics(img3214_path)

```

Step 5: Drag in the participation rate file to create a union with the labour force share file and edit the relationship as shown below.

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3215_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.2.1.5.png"
include_graphics(img3215_path)

```

Step 6: To obtain the participation rate in %, click on the drop down and create a calculated field as shown below. 

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3216_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.2.1.6.png"
include_graphics(img3216_path)

```

Step 7: For both data in step 6 and 3, change the data type for "Year" to date as shown below.

```{r, echo=FALSE, message=FALSE, out.width="25%", out.height="25%"}
library(knitr)
library(png)
img3217_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.2.1.7.png"
include_graphics(img3217_path)

```

Step 8: Add new data source to import median age data obtained from 3.1.3 (step 2). Similar to step 7, change the data type for "Year" to date.

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3218_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.2.1.8.png"
include_graphics(img3218_path)

```


### 3.2.2	Creation of charts to show shares of resident labour force

##### Do steps 1 - 5 to create visualisation for 2019 labour force data, and steps 6 - 8 for comparison with 2009 and 2014.

Step 1: Open a new Tableau worksheet. Drag "Shares (%)" to "Columns", "Age (group)" to "Rows" and "Year" to filter marks card. In the filter, select "Year", then "Next" and check the box for 2019. 

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3221_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.2.2.1.png"
include_graphics(img3221_path)

```

Step 2: Drag "Shares (%)" to the text marks card, click the green pill, select "format" to format the labeling of the bars.

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3222_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.2.2.2.png"
include_graphics(img3222_path)

```

Step 3: (To do formatting of the chart e.g. remove the grid lines etc) Click on the x-axis and select "format" and select "None" for the Grid lines under "Sheet", "Columns" and "Rows".

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3223_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.2.2.3.png"
include_graphics(img3223_path)

```

Step 4: Click on the x-asix and un-tick "Show Header".

```{r, echo=FALSE, message=FALSE, out.width="50%", out.height="50%"}
library(knitr)
library(png)
img3224_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.2.2.4.png"
include_graphics(img3224_path)

```

Step 5: Click on colour in the marks card and select the colour for the bar.

```{r, echo=FALSE, message=FALSE, out.width="50%", out.height="50%"}
library(knitr)
library(png)
img3225_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.2.2.5.png"
include_graphics(img3225_path)

```

Step 6: Go to "Data Source" sheet and create 2 calculated fields as shown below.

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3226_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.2.2.6.png"
include_graphics(img3226_path)

```

Step 7: Create another 2 calculated fields to obtain the change in percentage points since 2009 and 2014.

```{r, echo=FALSE, message=FALSE}
library(knitr)
library(png)
img3227_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.2.2.7.png"
include_graphics(img3227_path)

```

Step 8: Open a new Tableau worksheet. Drag "Percentage Change wrt 2009" and "Percentage Change wrt 2014" into "Columns" and "Age (group)" into Rows" as shown below. Ensure that "Bar" is being selected at the marks card. Drag "Percentage Change wrt 2009" and "Percentage Change wrt 2014" into their respective Text marks card for the label to appear and format the label to show in "pp" (similar to step 2). Ensure that the range for both charts are the sam by clicking on the x-axis, then click "Edit axis". Click on the x-axis and y-axis and un-tick "Show Header" to hide the axis. Drag "Percentage Change wrt 2009" and "Percentage Change wrt 2014" into colour marks card to format the colour of the bar as shown below. 

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3228_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.2.2.8.png"
include_graphics(img3228_path)

```


### 3.2.3	Creation of Charts to show participation rate

##### Repeat the steps in 3.2.2 (steps 1 - 5) to create visualisation for 2019 participation rate, and the steps in 3.2.2 (steps 6 - 8) for comparison with 2009 and 2014.

Step 1 - 5: Repeat the steps in 3.2.2 (steps 1 - 5) for participation rate data and the final visualisation is as below

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3231_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.2.3.1.png"
include_graphics(img3231_path)

```

Step 6 - 7: Repeat the steps in 3.2.2 (steps 6 - 7) with the following formula

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3232_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.2.3.2.png"
include_graphics(img3232_path)

```

Step 8: Repeat the steps in 3.2.2 (step 8) and the final visualisation is as below

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="120%", out.height="120%"}
library(knitr)
library(png)
img3233_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.2.3.3.png"
include_graphics(img3233_path)

```


### 3.2.4	Creation of Charts to show median age trend

Step 1: Open a new Tableau worksheet and select data source "Median Age". Drag "Year" into "Columns", "Median Age" into "Rows" and Text marks card to obtain the following chart (ensure to select Line in the marks card)

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", out.width="90%", out.height="90%"}
library(knitr)
library(png)
img3241_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/3.2.4.1.png"
include_graphics(img3241_path)

```


# 4.0 Final Data Visualisation Output

### Data Visualisation Link (Tableau Online)
https://public.tableau.com/views/DataVizMakeoverSingaporesResidentLabourForcein2019/FinalDashboard?:language=en&:display_count=y&:origin=viz_share_link

```{r, echo=FALSE, message=FALSE, out.width="200%", out.height="200%"}
library(knitr)
library(png)
img4_path <- "/awljiang/blog/_posts/2021-01-25-dataviz-makeover-01/data/4.3_final design.png"
include_graphics(img4_path)

```

### Major Insights

```{r, echo=FALSE, message=FALSE}
library("readxl")
library(kableExtra)

insights <- read_excel("D:\\awljiang\\blog\\_posts\\2021-01-25-dataviz-makeover-01\\data\\4_insights.xlsx")  
insights_2 <- data.frame(insights)

kbl(insights_2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left") %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, border_right = T, width = "50em") 

```


